---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
Title <- "The effectiveness of population-wide screening in reducing SARS-CoV-2 infection prevalence in Slovakia"
```

# The effectiveness of population-wide screening in reducing SARS-CoV-2 infection prevalence in Slovakia

This repository contains the data and code for our manuscript:

Pavelka S, Van-Zandvoort K, Abbott S, Sherratt K, Majdan M, CMMID COVID-19 working group, Jarčuška P, Krajčí M, Flasche S, Funk S,  _`r Title`_.

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/sbfnk/covid19.slovakia.mass.testing/archive/master.zip>

Or you can install this compendium as an R package, `covid19.slovakia.mass.testing`, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("sbfnk/covid19.slovakia.mass.testing")
```

### Included data sets

The repository contains three data sets:

The testing data set `ms.tst` can be loaded with
```{r mstst, eval = FALSE}
data(ms.tst)
```

Incidence of cases confirmed by PCR per county `PCR.inc` can be accessed with
```{r pcrinc, eval = FALSE}
data(PCR.inc)
```

The `Rt.county` data set contains the estimated median reproduction number in each county on 22 October 2020. 

```{r Rt.county, eval = FALSE}
data(Rt.county)
```

This data set can be re-created using the The [EpiNow2](https://epiforecasts.io/EpiNow2/) R package by running (noting that it can take a long time to run depending on the hardware available).

```{r reproduce_r, eval = FALSE}
source(here::here("data-raw", "scripts", "rt.r"))
source(here::here("data-raw", "scripts", "convert_data.r"))
```

The [EpiNow2](https://epiforecasts.io/EpiNow2/) R package that is used to estimate the reproduction numbers uses generation times and delay distributions saved in `data-raw/data`. They can be re-generated by running.

```{r reproduce_r, eval = FALSE}
source(here::here("data-raw", "scripts", "rt-distributions.r"))
```

The Google mobility data set for Slovakia `mob_slo` visualised in Supplementary Figure S4 can be accessed with

```{r mob_slo, eval = FALSE}
data(mob_slo)
```

### Figures and tables

To regenerate Table 1 and the adjusted prevalence risk ratio estimate, run

```{r regression, eval = FALSE}
r <- regression("table1.pdf")
r$round
```

To regenerate Fig. 1, run
```{r pcr_incidence, eval = FALSE}
pcr_incidence()
```

To regenerate Fig. 2, run
```{r risk_ratios, eval = FALSE}
rr <- risk_ratios()
rr$figures$a
rr$figures$b
rr$tables
```

To regenerate Fig. S4, run
```{r mobility, eval = FALSE}
mobility()
```

### Minimum specificity

To estimate minimum specificity, run
```{r min_spec}
estimate_min_specificity()
```
